How to compute the fusion product of MV cycles in type A

### 2021-04-09 draft.tex
whered we leaf off yest
minor edits

\section{Introduction}
% 
% The Mirkovi\'c--Vybornov isomorphism
In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov provide a geometric version of symmetric and skew Howe $(\GL_m,\GL_n)$ dualities by relating Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ on the one hand to slices in $n\times n$ nilpotent orbits 
% conjugacy classes of nilpotent matrices 
and on the other hand to Nakajima quiver varieties. 
This article generalizes the first of these relations (an isomorphism) to families by way of the Beilinson--Drinfeld Grassmannian. Essential to \cite{mirkovic2007geometric}, this space is used to define a fusion (aka convolution) product on sheaves (representations) but can also be used to define a fusion product of MV cycles (bases). 
% 
This product structure makes the vector space spanned by the MV cycles into a commutative algebra isomorphic to the ring of functions on the unipotent subgroup (conjectured in \cite{anderson2003polytope} and proved in \cite{baumann2019mirkovic}). % conjectured by JEA and proved by BKK
% 
To quote from Mirkovic and Vilonen:
\begin{quotation}
    However, we make crucial use of an idea of Drinfeld, going back to around 1990. He discovered an elegant way of obtaining the commutativity constraint by interpreting the convolution product of sheaves as a ``fusion'' product.
\end{quotation}
% 
[Liaison]

@@

\subsection{Some subvarieties of affine Grassmannians}
Now fix effective dominant coweights $\lambda', \lambda'' \in P_{++}$ of sizes $N',N''$  and their sums $ \lambda = \lambda' + \lambda'' $ of size $ N = N'+N''$. 
% Coweights define elements in the various affine Grassmannians which we consider. Warning: We will write only coset representatives for elements of the various Grassmannians; we hope that it is evident which right cosets they represent. 
% the right cosets which they represent are clear from the context.
We consider the following subschemes of the affine Grassmannians.
% 
\begin{definition}
    The \textbf{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $ a \textbf{spherical Schubert variety}.  
\end{definition}
    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    Note, since $ \lambda $ is effective, $ t^\lambda \in \Gr^+ $ and so the spherical Schubert variety $\overline{\Gr}^\lambda $ lies inside the positive part $ \Gr^+$ of the affine Grassmannian. \acom{why and so? cuz orbits are connected?}
    % 
\begin{definition} 
    The \textbf{fusion of two spherical Schubert varieties} 
    $$ 
    \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA \,.
    $$
\end{definition}
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda'}\times\overline\Gr^{\lambda''}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}
    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} $ for $ s \ne 0 $ is $ \overline{\Gr}^{\lambda'} \times \overline{\Gr}^{\lambda''}$.  
    % By \cite[Proposition 3.1.14]{zhu2016introduction},
    % Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
    % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
    Over $s=0$ the fibre is $ \overline{\Gr}^{\lambda' + \lambda''}$ (and reduced) by 
    % a theorem of Zhu 
    \cite[Proposition 3.1.14]{zhu2016introduction}.

@@

>>>>

\section{Introduction}
% 
% The Mirkovi\'c--Vybornov isomorphism
In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov provide a geometric version of symmetric and skew Howe $(\GL_m,\GL_n)$ dualities by relating Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ to slices in $n\times n$ nilpotent orbits on the one hand 
% conjugacy classes of nilpotent matrices 
and to Nakajima quiver varieties on the other hand. 
This paper generalizes the first of these relations (an isomorphism) to families of slices by way of the Beilinson--Drinfeld Grassmannian. 
Essential to \cite{mirkovic2007geometric}, this space is used to define a fusion (aka convolution) product on sheaves (representations) but can also be used to define a fusion product of MV cycles (bases). 
% 
This product structure makes the vector space spanned by the MV cycles into a commutative algebra isomorphic to the ring of functions on the unipotent subgroup (conjectured in \cite{anderson2003polytope} and proved in \cite{baumann2019mirkovic}). % conjectured by JEA and proved by BKK
% 
To quote from Mirkovic and Vilonen:
\begin{quotation}
    However, we make crucial use of an idea of Drinfeld, going back to around 1990. He discovered an elegant way of obtaining the commutativity constraint by interpreting the convolution product of sheaves as a ``fusion'' product.
\end{quotation}
% 
[Liaison]

@@

\subsection{Some subvarieties of affine Grassmannians}
Now fix effective dominant coweights $\lambda', \lambda'' \in P_{++}$ of sizes $N',N''$  and their sums $ \lambda = \lambda' + \lambda'' $ of size $ N = N'+N''$. 
% Coweights define elements in the various affine Grassmannians which we consider. Warning: We will write only coset representatives for elements of the various Grassmannians; we hope that it is evident which right cosets they represent. 
% the right cosets which they represent are clear from the context.
We consider the following subschemes of the affine Grassmannians.
% 
\begin{definition}
    The \textbf{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $ a \textbf{spherical Schubert variety}.  
\end{definition}
    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    Note, since $ \lambda $ is effective, $ t^\lambda \in \Gr^+ $ and so the spherical Schubert variety $\overline{\Gr}^\lambda $ lies inside the positive part $ \Gr^+$ of the affine Grassmannian. \acom{why ``and so''? bc orbits are connected?}
    % 
\begin{definition} 
    The \textbf{fusion of two spherical Schubert varieties} 
    $$ 
    \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA \,.
    $$
\end{definition}
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda'}\times\overline\Gr^{\lambda''}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}
    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} $ for $ s \ne 0 $ is $ \overline{\Gr}^{\lambda'} \times \overline{\Gr}^{\lambda''}$.  
    % By \cite[Proposition 3.1.14]{zhu2016introduction},
    % Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
    % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
    Over $s=0$ the fibre is $ \overline{\Gr}^{\lambda' + \lambda''}$ (and reduced) by 
    % a theorem of Zhu 
    \cite[Proposition 3.1.14]{zhu2016introduction}.

@@

\subsection{Pseudocode}
